Decoding Consumer Preferences with Large Language Models: A Novel Training Framework

### 2024-05-15 meetings/summary.qmd
1-slide pitch

---
title: "BDS MPhil: Reverse Engineering GPT"
author: "Finn-Ole Höner; Supervisors: Bas Donkers, Dennis Fok"
date: last-modified
date-format: long
format: beamer
aspectratio: 169
incremental: false
pdf-engine: pdflatex
include-in-header: ../beamer_preamble.tex
bibliography: ../references.bib
fig-align: center
fig-cap-location: bottom
fig-format: pdf
links-as-notes: true
number-depth: 1
eval: false
echo: true
fig-width: 12
fig-height: 8
---

@@

- Optimize optimization process.
- Enhance generation mode for clearer new claims.
- Integrate consumer preferences/ratings for generated claims.
---

>>>>

---
title: "BDS MPhil"
author: "Finn-Ole Höner; Supervisors: Bas Donkers, Dennis Fok"
date: last-modified
date-format: long
format: beamer
aspectratio: 169
incremental: false
pdf-engine: pdflatex
include-in-header: ../beamer_preamble.tex
bibliography: ../references.bib
fig-align: center
fig-cap-location: bottom
fig-format: pdf
links-as-notes: true
number-depth: 1
eval: false
echo: true
fig-width: 12
fig-height: 8
---

# Decoding Marketers' Intentions: Deterministic Generation of Ad-Claims

::: {.columns}
::: {.column}

**Setting**

- Advertising claims with meta information & ratings

**Contribution**

- Novel "summary embeddings", that make an LLM generate a specific ad-claim.

**What's done?**

- Algorithm, validation, data acquisition, Snellius application

**What's next?**

- Empirical application, first-draft

<!--

- Match and mismatch of intention and wording?

- Comparing focal brand with competitors, country, consumer ratings, brand fit, different languages, ranking of claims within set, compare branded and unbranded, sustainability messages, tangible & intangible

- Different sub-categories of hair-care e.g. intense damage, hydro, color

- mixtures of certain phrasings

Using model for prediction? Have training claims and test claims embedded in the same space. Then use the training claims to predict the test claims based on encoding space.

male and female targeting

short-term, long-term benefits

fit with brand measure

Pre-training based on GPT generated claims

Dairy: Naturality, nutrition, ingredients, ferments
-->

:::
::: {.column}
![2D-generation space.](./figures/slides_pitch.png)
:::
:::

@@

- Optimize optimization process.
- Enhance generation mode for clearer new claims.
- Integrate consumer preferences/ratings for generated claims.

---

### 2024-05-15 writing/paper.qmd
1-slide pitch

---
author: Finn-Ole Höner (657110)
title: "Decoding Consumer Preferences with Large Language Models: A Novel Training Framework"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 20mm
            - bottom = 20mm
            - left = 20mm
            - right = 20mm
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
---

@@

@@

# Theory

- Generative AI for text
    - Attention
    - Transformer
    - GPT

- Maximize the likelihood to generate the data

The Autoencoder $\operatorname{AE}_{\mathcal{B}} \left(\cdot \right): \lbrace 0, 1 \rbrace^{C} \to \mathbb{R}^E$, with parameters $\mathcal{B}$

The log-likelihood function $\operatorname{\mathcal{L}} \left ( \cdot \right): \mathbb{R}^E \to \left (- \infty, 0 \right]$

The length $E$ summary-embedding $\boldsymbol{e}$.

The length $T$ vector of target tokens $\boldsymbol{t}$, where the element $t_i$ is a unique integer code representing a token, e.g. in GPT-2, $50267$ is the End-of-Text token `<|eos|>`.

@@

- Adding covariates to the AE

@@

<!-- TODO: Consider renaming this headline -->
# Implementation

@@

- Generative AI for personalization
- Brands
- Wording

@@

- Expansion of this research
  - MAB around the fitted AE, to incorporate consumer feedback in online learning: Which areas of the space are valuable for which consumers?
  - Better LLM
  - Image, video, website, audio data. Perhaps website a good application. Perhaps audio a rather simple way to make this multi-modal (content and sound)

>>>>

---
author: Finn-Ole Höner (657110)
title: "Decoding Consumer Preferences with Large Language Models: A Novel Training Framework"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 1in
            - bottom = 1in
            - left = 1in
            - right = 1in
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
---

@@

- Comparison to prompt engineering

@@

# Methodology

- Overview
  - LLM
  - maximize likelihood of target sequence
  - autoencoder on these summary embeddings (+ covariates?)
  - also yields low-dim generation space
  - generation
  - rating of claims

- LLM
  - Attention
  - Transformer
  - GPT
  - The length $E$ summary-embedding $\boldsymbol{e}$.
  - The length $T$ vector of target tokens $\boldsymbol{t}$, where the element $t_i$ is a unique integer code representing a token, e.g. in GPT-2, $50267$ is the End-of-Text token `<|eos|>`.

- Maximize the likelihood to generate the data
  - The log-likelihood function $\operatorname{\mathcal{L}} \left ( \cdot \right): \mathbb{R}^E \to \left (- \infty, 0 \right]$

@@

- Autoencoder
  - The Autoencoder $\operatorname{AE}_{\mathcal{B}} \left(\cdot \right): \lbrace 0, 1 \rbrace^{C} \to \mathbb{R}^E$, with parameters $\mathcal{B}$
  - Adding covariates to the AE

- Figure of generation tree
  - beam-search for generation

@@

## Implementation

@@

- Generative AI for personalization

- Brands

- Wording

- Interactive dashboard to explore the embedding space

@@

- Expansion of this research
  - MAB around the fitted AE, to incorporate consumer feedback in online learning: Which areas of the space are valuable for which consumers?
  - For online learning, could wrap the decoder into an MAB and let the MAB explore the space by pulling arms <!-- TODO: Which kind of MAB? -->
  - Could also learn preferences online with this setup
  - Better LLM
  - Image, video, website, audio data. Perhaps website a good application. Perhaps audio a rather simple way to make this multi-modal (content and sound)
